### 2020-06-03 sections/major/major.tex
added couple of comments / minor changes + fixed operations fig

Magic is commonly quantified via monotones \nick{CITE}. 
A monotone is a projection from the $d$-dimensional set of density states of the theory to the real line. 
It is monotonically decreasing under free operations, reflecting the no resource generating property of free operations and thus respecting the pre-order $\prec$ of the theory.
A popular magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
\end{equation}
However, a single monotone does not provide information on whether two states are incomparable in the theory.
Motivated by this restrictive nature of the monotone, we introduce the idea of a \emph{fragment} as a less restrictive way of comparing the resource of states in an arbitrary theory $\R = (\F, \O)$. \nick{explain exactly why fragments $>$ monotones}
Let $\R' = (\F', \O')$ be a subtheory of $\R$ so that $\F' \subseteq \F$ and $\O' \subseteq \O$. 
Then, we define a fragment as follows.
\begin{definition}\label{def:fragment}
    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
    We call a resource fragment of $\R$ any theory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$, if there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
    \begin{enumerate}
        \item $\Pis: \F \mapsto \F'$ and $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ whenever $\rho_1 \prec_{\R} \rho_2$ for any states $\rho_1, \rho_2 \in \F$;
        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for any free operations $\E_1, \E_2 \in \O$. 
    \end{enumerate}
\end{definition}
The subtheory $\R'$ is essentially the image of the surjection $\Pi$.
The point of constructing a resource fragment with such a surjective map would be to achieve a more convenient set of free states or operations, or importantly a more convenient pre-order.

@@

Our goal is to give insight into magic state transformations.
We first break up the theory into fragments that allow for the incorporation of $\bmd$-majorization in its framework.
\begin{definition}\label{def:sigmafrag}
    A subtheory $\R'$ of the Wigner negativity theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that preserve $\sigma$,
    \begin{equation}
        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \}.
    \end{equation}
\end{definition}

@@

    Conversely, suppose $\E$ is in $\O$. 
    The free states are mapped one-to-one to a subset $\cal{S}$ of the $(d^2 - 1)$-dimensional probability simplex.
    $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
    Therefore, $\cal{S}$ is convex and compact as a convex subset of the bounded compact probability simplex.
    Then, $\W{\E}{}$ is a stochastic, thus continuous, mapping from $\cal{S}$ to itself and Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $g_{\bmz}, \bmz \in \pd$ that is preserved by $\W{\E}{}$.
    This corresponds one-to-one to a state $\sigma \coloneqq \sum_{\bmz \in \pd} g_{\bmz} A_{\bmz}$ and so $\O \subseteq \bigcup\limits_{\sigma \in \F} \O_\sigma$.

>>>>

Magic is commonly quantified via monotones \nick{CITE}. 
A monotone is a projection from the $d$-dimensional set of density states of the theory to the real line. 
It is monotonically decreasing under free operations, reflecting the no resource generating property of free operations and thus respecting the pre-order $\prec$ of the theory.
A popular magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
\end{equation}
However, a single monotone does not provide information on whether two states are incomparable in the theory.
Motivated by this restrictive nature of the monotone, we introduce the idea of a \emph{fragment} as a less restrictive way of comparing the resource of states in an arbitrary theory $\R = (\F, \O)$. \nick{explain exactly why fragments $>$ monotones}
Let $\R' = (\F', \O')$ be a subtheory of $\R$ so that $\F' \subseteq \F$ and $\O' \subseteq \O$. 
Then, we define a fragment as follows.
\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
    We call a resource fragment of $\R$ any theory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$, if there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
    \begin{enumerate}
        \item $\Pis: \F \mapsto \F'$ and $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ whenever $\rho_1 \prec_{\R} \rho_2$ for any states $\rho_1, \rho_2 \in \F$;
        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for any free operations $\E_1, \E_2 \in \O$. 
    \end{enumerate}
    We call $\Pi$ a resource projection.
\end{definition}
The subtheory $\R'$ is essentially the image of the surjection $\Pi$.
The point of constructing a resource fragment with such a surjective map would be to achieve a more convenient set of free states or operations, or importantly a more convenient pre-order.

@@

Our goal is to give insight into magic state transformations.
We first break up the theory into fragments that allow for the incorporation of $\bmd$-majorization in its framework.
\begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
    A subtheory $\R'$ of the Wigner negativity theory $\R = (\F, \O)$ is called a \emph{$\sigma$-fragment} iff $\R' = (\F, \O_\sigma)$, where the free operations are restricted to the ones that preserve $\sigma$,
    \begin{equation}
        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \}.
    \end{equation}
\end{definition}

@@

    Conversely, suppose $\E$ is in $\O$. 
    The free states are mapped one-to-one to a subset $\cal{S}$ of the $(d^2 - 1)$-dimensional probability simplex.
    $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
    Therefore, $\cal{S}$ is convex and compact as a convex subset of the bounded compact probability simplex. \nick{Need to prove that $\cal{S}$ is closed.}
    Then, $\W{\E}{}$ is a stochastic, thus continuous, mapping from $\cal{S}$ to itself and Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $g_{\bmz}, \bmz \in \pd$ that is preserved by $\W{\E}{}$.
    This corresponds one-to-one to a state $\sigma \coloneqq \sum_{\bmz \in \pd} g_{\bmz} A_{\bmz}$ and so $\O \subseteq \bigcup\limits_{\sigma \in \F} \O_\sigma$.
